### 2019-02-27 soc.tex
update references to equations formatting
update table formatting
This fixes the bottom rule being thicker than the top one.

Interestingly, only removing the \hline doesn't solve the problem, but changing the heavyrulewidth does.

% TABLES          %
% requires: float %
%-===============-%
\floatstyle{plaintop}                           % table caption on top
\restylefloat{table}                            % -||-
\usepackage{booktabs}                           % table formatting

@@

  Příkladem zápisu matematiky v článku je rovnice~\ref{eq:katex equation}, která je pomocí \KaTeX u převedena na rovnici~\ref{eq:converted equation}.

@@

  \begin{tabular}{*5l}  \toprule

@@

    Hong Kong, China        & \href{https://www.webpagetest.org/result/190213_NK_dfd8ddf4b9766b3386799de124a67ad8}{\texttt{190213\_NK\_dfd8ddf4b9766b3386799de124a67ad8}} \\ \bottomrule \hline

>>>>

% TABLES          %
% requires: float %
%-===============-%
\floatstyle{plaintop}                           % table caption on top
\restylefloat{table}                            % -||-
\usepackage{booktabs}                           % table formatting
\setlength\heavyrulewidth{0.25ex}

@@

  Příkladem zápisu matematiky v článku je rovnice~(\ref{eq:katex equation}), která je pomocí \KaTeX u převedena na rovnici~(\ref{eq:converted equation}).

@@

  \begin{tabular}{*5l}
    \toprule

@@

    Hong Kong, China        & \href{https://www.webpagetest.org/result/190213_NK_dfd8ddf4b9766b3386799de124a67ad8}{\texttt{190213\_NK\_dfd8ddf4b9766b3386799de124a67ad8}} \\
    \bottomrule
